\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-12 doc/publications/plos16/plos16.tex
added abstract to plos16.tex

\newcommand{\cursedforest}{\textsc{CursedForest}\xspace}
\newcommand{\mtry}{\texttt{mtry}\xspace}
\newcommand{\ntree}{\texttt{ntree}\xspace}

@@

% Please keep the abstract below 300 words
\section{Abstract}
The abstract.

@@

The most popular random forest software packages are R-based, although current implementations do not scale well with
increasing feature size~\cite{Wright.and.Ziegle.2016}.  This is despite R now supporting long vectors (length greater
than $2^{31}-1$), and the \textsc{randomForest} implementation in R lending itself to parallelization to grow multiple
trees simultaneously~\cite{Liaw.and.Weiner.2002} and them combine them.  More suitable implementations for ``wide''
genomic data have been developed in other programming languages. \textsc{CloudForest} \cite{Bressler2015} written in Go,
achieves fast run times by effective use of the CPU cache, optimizing for different classes of features and efficiently
multi-threading.  Similarly, \textsc{Ranger}~\cite{Wright.and.Ziegle.2016} written in C++ with an R front-end is
specifically optimized for dealing with large data sets.

>>>>

\newcommand{\cursedforest}{\textsc{CursedForest}\xspace}
\newcommand{\ranger}{\textsc{Ranger}\xspace}
\newcommand{\mtry}{\texttt{mtry}\xspace}
\newcommand{\ntree}{\texttt{ntree}\xspace}

@@

% Please keep the abstract below 300 words
\section{Abstract}
We introduce \cursedforest, an implementation of random forests designed to handle data that may have an extremely large
number of variables. We discuss the utility of random forests for machine learning problems. We show on simulated and
real data that the novel implementation can achieve reasonable prediction accuracy and variable importance estimates
even in setting where other implementations, including some designed for large data, fail.

@@

The most popular random forest software packages are R-based, although current implementations do not scale well with
increasing feature size~\cite{Wright.and.Ziegle.2016}.  This is despite R now supporting long vectors (length greater
than $2^{31}-1$), and the \textsc{randomForest} implementation in R lending itself to parallelization to grow multiple
trees simultaneously~\cite{Liaw.and.Weiner.2002} and them combine them.  More suitable implementations for ``wide''
genomic data have been developed in other programming languages. \textsc{CloudForest} \cite{Bressler2015} written in Go,
achieves fast run times by effective use of the CPU cache, optimizing for different classes of features and efficiently
multi-threading.  Similarly, \ranger~\cite{Wright.and.Ziegle.2016} written in C++ with an R front-end is
specifically optimized for dealing with large data sets.
